### 2024-11-11 conteudo/background/linux.tex
changes on linux

One of the subsystems within the Linux kernel is the AMD Display Driver, which
is responsible for implementing the drivers needed for AMD GPUs to function
correctly in a Linux environment. The maintainers of this subsystem have
reported a practical issue: a significant amount of duplicated code, which
complicates the maintenance of this subsystem. This problem serves as the
starting point for our research, with the AMD Display Driver as our primary
object of study as we aim to understand and mitigate code duplication in the
Linux kernel. The AMD Display Driver subsystem contains more then 391000 lines 
of code and more then 1089 code files
\footnote{ 
Data extracted directly from the Linux repository with the help of the cloc tool.
\citep{cloc}
}, 
making it a considerable component within the Linux kernel. Like other 
subsystems, discussions about the AMD Display Driver are conducted on its 
designated mailing list.

\todo[inline]{FIND MAILING LIST AND CITE HERE}

>>>>

One of the subsystems within the Linux kernel is the AMD Display Driver, which
is responsible for implementing the drivers needed for AMD GPUs to function
correctly in a Linux environment. The maintainers of this subsystem have
reported a practical issue: a significant amount of duplicated code, which
complicates the maintenance of this subsystem. This problem serves as the
starting point for our research, with the AMD Display Driver as our primary
object of study as we aim to understand and mitigate code duplication in the
Linux kernel. The AMD Display Driver subsystem contains more then 391000 lines 
of code and more then 1089 code files
\footnote{ 
Data extracted directly from the Linux repository with the help of the cloc tool.
\citep{cloc}
}, 
making it a considerable component within the Linux kernel. Like other 
subsystems, discussions about the AMD Display Driver are conducted on its 
designated mailing list, which can be accessed here: 
\url{https://lists.freedesktop.org/mailman/listinfo/amd-gfx}.

\todo[inline]{FIND MAILING LIST AND CITE HERE (DONE?) }
